Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models

### 2020-10-15 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, add one more figure.

As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's
Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
The dropout rate is $0.05$.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 6	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
\hline
RBT3   & CIFAR-100 & 6	&	93.71\% \\
RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

>>>>

As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's
Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 512 and train for $6\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
The dropout rate is $0.05$.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 6	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
\hline
RBT3   & CIFAR-100 & 12	&	99.66\% \\
RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}
